### 2024-10-24 manuscript.tex
Minor edits

PK and FB received funding from the European Union’s Horizon 2020 research and
innovation program under a grant agreement no. 101003470. Supercomputing
resources were provided by the DKRZ (project 1125 ICON-development) and the
National Academic Infrastructure for Supercomputing in Sweden (allocation
2023/22-202).  We acknowledge the RV \emph{Polarstern} datasets provided by the
Alfred Wegener Institute and Pangaea, the AA15-16 dataset provided by the
Australian Antarctic Division (AAD) and University of Canterbury (UC), RV
\emph{Tangaroa} datasets provided by the National Institute of Water and
Atmospheric Research and UC, the NBP1704 dataset provided by the National
Science Foundation, Cooperative Institute for Research in Environmental
Sciences, University of Colorado and UC, the HMNZSW16 dataset provided by the
Royal New Zealand Navy and UC, the MARCUS dataset provided by the Atmospheric
Radiation Measurement (ARM) and AAD, and the MICRE dataset provided by ARM, the
Australian Bureau of Meteorology, and AAD. We thank the scientific staff, the
crew, and everyone involved in collecting data on the voyages and stations,
especially Kelly Schick, Peter Guest, John J.  Cassano, Simon Parsons, Graeme
Plank, Sally Garrett, Jamie Halla, Sean Hartery, Mike J.  Harvey (†), Simon P.
Alexander, and Alex Schuddeboom. We acknowledge the ICON model output provided
by the nextGEMS project and the DKRZ, reanalysis dataset ERA5 provided by the
Copernicus Climate Change Service and MERRA-2 provided by the Global Modeling
and Assimilation Office.  Last but not least, we acknowledge the use of open
source software Python, Cython \citep{behnel2011}, TensorFlow
\citep{abadi2016}, Devuan GNU+Linux, parallel \citep{tange2011}, NumPy
\citep{harris2020}, SciPy \citep{virtanen2020}, Matplotlib \citep{hunter2007},
cartopy \citep{cartopy}, pyproj, Inkscape, Bash, GNU Fortran, HDF
\citep{folk1999}, and NetCDF \citep{rew1990}.  We dedicate this study to the
memory of Mike J.  Harvey, who very substantially contributed to obtaining the
atmospheric observations on the RV \emph{Tangaroa} voyages used in this study.

>>>>

PK and FB received funding from the European Union’s Horizon 2020 research and
innovation program under a grant agreement no. 101003470. Supercomputing
resources were provided by the DKRZ (project 1125 ICON-development) and the
National Academic Infrastructure for Supercomputing in Sweden (allocation
2023/22-202). We acknowledge the contribution of Thorsten Mauritsen to funding
acquisition and project management.  We acknowledge the RV \emph{Polarstern}
datasets provided by the Alfred Wegener Institute and Pangaea, the AA15-16
dataset provided by the Australian Antarctic Division (AAD) and University of
Canterbury (UC), RV \emph{Tangaroa} datasets provided by the National Institute
of Water and Atmospheric Research and UC, the NBP1704 dataset provided by the
National Science Foundation, Cooperative Institute for Research in
Environmental Sciences, University of Colorado and UC, the HMNZSW16 dataset
provided by the Royal New Zealand Navy and UC, the MARCUS dataset provided by
the Atmospheric Radiation Measurement (ARM) and AAD, and the MICRE dataset
provided by ARM, the Australian Bureau of Meteorology, and AAD. We thank the
scientific staff, the crew, and everyone involved in collecting data on the
voyages and stations, especially Kelly Schick, Peter Guest, John J.  Cassano,
Simon Parsons, Graeme Plank, Sally Garrett, Jamie Halla, Sean Hartery, Mike J.
Harvey (†), Simon P.  Alexander, and Alex Schuddeboom. We acknowledge the ICON
model output provided by the nextGEMS project and the DKRZ, reanalysis dataset
ERA5 provided by the Copernicus Climate Change Service and MERRA-2 provided by
the Global Modeling and Assimilation Office.  Last but not least, we
acknowledge the use of open source software Python, Cython \citep{behnel2011},
TensorFlow \citep{abadi2016}, Devuan GNU+Linux, parallel \citep{tange2011},
NumPy \citep{harris2020}, SciPy \citep{virtanen2020}, Matplotlib
\citep{hunter2007}, cartopy \citep{cartopy}, pyproj, Inkscape, Bash, GNU
Fortran, HDF \citep{folk1999}, and NetCDF \citep{rew1990}.  We dedicate this
study to the memory of Mike J.  Harvey, who very substantially contributed to
obtaining the atmospheric observations on the RV \emph{Tangaroa} voyages used
in this study.
